---
title: "R Notebook"
output: html_notebook
---


I.CREATE A VECTOR
======================
##1. Create a vector from data composition
```{r}
#Vector
vectNumerico<-c(3,1,5,6,3,9)

vectNumerico1<-c(2:8)

vectString<-c("jose","jesus","walter","Jonh","Julio","Pieree")
vectString
```

##2. Create a vector from secuence and repetitions
```{r}
## a) ( 1,2,3, ??? ,19,20) 
v1<-c(1:20)

## b) ( 20,19, ??? ,2,1 )
v2<-c(20:1)

## c) ( 1,2,3, ??? ,19,20,19,18, ??? ,2,1 )
v3<-c(1:20,19:1)

## d) (4,6,3) y asignarlo a la variable tmp
tpm<-c(4,6,3)

## e) ( 4,6,3,4,6,3, ??? ,4,6,3 ) donde el numero 4 aparece 10 veces.
v4<-rep.int(tpm,times=10)

#f) ( 4,6,3,4,6,3, ??? ,4,6,3,4 ) donde hay 11 ocurrencias del n?mero 4, 10 ocurrencias del n?mero 6 y 10 ocurrencias del n?mero 3
v5<-c(v4,4)
##g) ( 4,4, ??? ,4,6,6, ??? ,6,3,3, ??? ,3 ) donde hay 10 ocurrencias del numero 4, 20 ocurrencias del numero 6 y 30 ocurrencias del numero 3
v6<-rep(4,times=10)
v7<-rep(6,times=20)
v8<-rep(3,times=30)
v9<-c(v6,v7,v8)

vectSecuence<-seq(2, 4, by=0.5)

vectRepetition<-rep(1:2, times=3)
```

##3.Create vectors of date
```{r}
#1.Create a dataframe of dates 
df.dates<-seq(as.Date("1910/1/1"), as.Date("1999/1/1"), "years")
```




#3.Raw Data with "Date"
```{r}
data1 <- data.frame(a = abs(rnorm(20) * 10),
                  b = abs(rnorm(20) * 10),
                  date = seq(as.Date("2014-01-01"), by = "month", length.out = 20))
```

##3.1Date and seed
```{r}
set.seed(20)
deliver_Date<-Sys.Date()+sort(sample(1:5,3))
deliver_Date
```

```{r}
Start <- as.Date("2013-01-01")
End <- as.Date("2013-01-31")
dates <- seq(from = Start, to = End, by = 1)

set.seed(2)
draw1 <- sample(dates, 30)
draw2 <- sample(dates, 5)

draw1
```




II.CREATE A DATAFRAME
======================
##1.From vectors
```{r}
#one colum
df1<-data.frame(y = 1:5)

#Two columns Data frame without column name, base in previous vectors
df2<-data.frame(vectNumerico,vectString)

#Data frame with column name
df3<-data.frame(products=vectNumerico,peopleName=vectString)

```

##2.From scratch  
```{r}
#1.From vectors 
 col1 = c(2, 3, 5) 
 col2 = c("aa", "bb", "cc") 
 col3 = c(TRUE, FALSE, TRUE) 
 df4 = data.frame(col1, col2, col3)
 
 #2.Data frame with 3cols x 5rows
  df5 <- data.frame(Nombre=c("Melody","Gian","Johana","Jearson","Jenny"),scores=c(3,1,5,6,3),Menbership=c(11,2,6,7,8))
  

```



##3.Using letters
```{r}
col1 = c(letters[1:4],"m") #put the first 4 random letter and "m" as the last one
col2 = 1:5
col3 = letters[10:14]

data2 <- data.frame(col1,col2,col3)
```


##4 Using "seed"

```{r}
set.seed(1234)
"create a vector"
diag      = c("Depression", "Bipolar")
#create the datafrae
ID        = 1:10
Age       = round(rnorm(10, 50, 1))
Diagnosis = sample(diag, 10, replace=TRUE)

data = data.frame(ID, Age, Diagnosis)
```
s
```{r}
set.seed(99)
x1 <- rbinom(20, 1, 0.5)

set.seed(100)
x2 <- round(10 + rnorm(20, 5, 5), 2)

set.seed(101)
y <- round((1 + (x2 * 2 / 5) + x1 - rnorm(20, 0, 3)), 2)


rcart_df <- data.frame(x1, x2, y)
rcart_df
```

##5.Using "sample"
```{r}
myservice <- c("service1","service2","service3","service4")
mylevels <- c('Strongly Disagree', 'Disagree', 'Neither', 'Agree', 'Strongly Agree')

# Create a dummy data frame. Note that "Item 1" has only four levels
items <- data.frame('service'=factor(sample(myservice[1:4], 100, replace=TRUE)),
					'satisfaction'=factor(sample(mylevels[1:5], 100, replace=TRUE)),
					'Item 3'=factor(sample(mylevels[1:5], 100, replace=TRUE)),
					check.names=FALSE)
str(items)
```



##6.Create binary data 

```{r}
#expand.grid:Create a data frame from all combinations of the supplied vectors or factors
set.seed(123)
AND <- c(rep(0, 3), 1)

binary.data <-data.frame(expand.grid(c(0, 1), c(0, 1)), AND) 
```




##3. From a "R Data Librerias"
###3.1.Import datalibrary
```{r}
data("iris")

#Showing 4 first rows from iris dataset
head(iris,4)

#Showing 5 last rows from iris dataset
tail(iris,5)

#Assign to a variable
df5 <- head(iris,10)
df5
View(df5)

```

###3.1.Import datalibrary
```{r}
install.packages(c("nycflights13", "Lahman"))
library(nycflights13)
library(Lahman)
```

```{r}
nycflights13::airports
```

```{r}
df8=nycflights13::airports
df8
```


##4. From files inside a file server o PC

```{r}
#1. import library
install.packages("readxl")
library(readxl)

#2.upload the "prueba1.xlsx" file
df6<- read_excel("C:/R-Source/prueba1.xlsx")
View(df6)
```




IIi.LIST
===============
*Base on "R for data Science", by Hadley Wickham*

# 1.Create and show Lists
```{r}
L1 <- list(c(1, 4), c(8, 4))
L2 <- list(list(1, 8), list(7, 4))
L3 <- list(1, list(2, list(5)))


```

#2. Subsetting ("utils" packages)
```{r}
a <- list(a = 1:3, b = "a string", c = pi, d = list(-1, -5))

str(a[1:2])

```
#3.Assign values to a Dataframe
```{r}
exlist<-as.data.frame(a$a)
```

Iv.Setting a work space
=============
```{r}
setwd ( "C:/R-Source/bd_dashboard" )
```

