---
title: "R Notebook"
output: html_notebook
---

```{r}

if (!require("dplyr")) {
  install.packages("dplyr", repos="http://cran.rstudio.com/") 
  library(dplyr)
}

if (!require("readxl")) {
  install.packages("readxl", repos="http://cran.rstudio.com/") 
  library(readxl)
}

if (!require("stringr")) {
  install.packages("stringr", repos="http://cran.rstudio.com/") 
  library(stringr)
}

if (!require("htmlwidgets")) {
  install.packages("htmlwidgets", repos="http://cran.rstudio.com/") 
  library(htmlwidgets)
}

if (!require("officer")) {
  install.packages("officer", repos="http://cran.rstudio.com/") 
  library(officer)
}

```

I.Just text from .docx
====================
##1.Load a great deal of documents
The function docx_summary() returns the content of a Word document.
```{r}
dir <-"C:/R-Source/docs"
filenames <- list.files(path = dir, pattern = "*.docx", full.names = TRUE)
docxtest <- lapply(filenames, function(x) officer::docx_summary(officer::read_docx(x)) )
#turn "docxtest" (the content exttracted) into a data-frame
docxtest<-as.data.frame(docxtest)

View(docxtest)
```

##2.Resume
```{r}
#Return the First or Last Part of an Object
head(docxtest)
#Summary of objetc
tapply(docxtest$doc_index, 
       docxtest$content_type, 
       function(x)length(unique(x)))
```


##3.Getting all paragraphs:
```{r}

par_data <- subset(docxtest,content_type %in% "paragraph") 
par_data <- par_data[, c("doc_index", "style_name", 
                         "text", "level", "num_id") ]
par_data$text <- with(par_data, {
  substr(
    text, start = 1, 
    stop = ifelse(nchar(text)<30, nchar(text), 30) )
})
par_data
```

##4.Word tables
```{r}
table_cells <- subset(docxtest, content_type %in% "table cell")
print(head( table_cells) )
```


##5.Cells positions and values are dispatched in columns row_id, cell_id, text and is_header

```{r}
#(a logical column indicating if the cell is part of a header or not). Note that the content itself (column text) is a character vector.
table_body <- subset(table_cells, !is_header)
table_body <- table_body[,c("row_id", "cell_id", "text")]
head(table_body)
```

II.RESHAPING DATA
==============
##1.Reshaping the data close to the orginal table
```{r}
##with columns row_id, cell_id and text would display something close to the orginal table:
tapply(table_body$text, 
       list(row_id = table_body$row_id, 
            cell_id = table_body$cell_id
            ), 
       FUN = I
       )
```

##2.Getting headers requires another operation:
```{r}
data <- subset(table_cells, is_header) 
data <- data[, c("row_id", "cell_id", "text") ] 

tapply(data$text, 
   list(row_id = data$row_id, 
        cell_id = data$cell_id
        ), FUN = I )
```


##3.View the field which contain:
```{r}
View(docxtest$text[docxtest$row_id==27])
```


```{r}
#Is "X" before or after some expression like "Evento de Uso 1"  
"Evento de Uso 1 (Situaci?n no esperada para escalar a REAPRO)X"

pattern="Evento de Uso 1 (Situaci?n no esperada para escalar a REAPRO)X"
text_source= docxtest$text[docxtest$row_id==27]

str_detect(text_source,pattern)

str_view(text_source,"X")

grep(pattern,text_source)
```

```{r}
# Creae a vector variable and assign four string values ot the variable
strings <- c("abcd", "cdab", "cabd", "c abd")

# Find string values containing 'ab', return indices
grep("ab", strings)
```



s
```{r}
install.packages("sos")
library("sos")
findFn("word frequency")
```










