---
title: "R Notebook"
output: html_notebook
---


```{r}
data3=iris
#Way2: using ifelse(base library) .We cannot use a list of patterns whe we use "grepl"
data3$Species <- ifelse(grepl("setosa",data3$Species),"specie1","null")
```


# For 
```{r}
#create working data
data1 <- head(iris,10)

for(i in 1:nrow(data1)){
print(data1[i,1])
}


```



```{r}
section <- c("MATH111", "MATH111", "ENG111")
grade <- c(78, 93, 56)
student <- c("David", "Kristina", "Mycroft")
gradebook <- data.frame(section, grade, student)


mutate(gradebook, letter = ifelse(grade %in% 60:69, "D",
                                     ifelse(grade %in% 70:79, "C",
                                            ifelse(grade %in% 80:89, "B",
                                                   ifelse(grade %in% 90:99, "A", "F")))))



```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
